\vskip-0.6in \Large Political Uncertainty

### 2016-02-09 two-groups.tex
add obj fcn for vote buyer A; fix Z,Y mixup up to sec:nonneg

\newpage
\section{Solving the Model}
\label{sec:solve}
Backward induction (legislature moves last; B makes last bribe; A makes first bribe)
\begin{enumerate}
	\item Legislature
		\begin{itemize}
			\item Each legislator $z$ will decide whether to vote for $x$ or $s$ given $z$, $a(z)$ and $b(z)$. Votes for $x$ if
			  \[
				  v(z) = \alpha -\beta z + \ve_z + a(z) - b(z)
				\]
				(whether the inequality is weak or strict depends on tie-breaking rules set out in the paper)
					\begin{itemize}
						\item Notice that a bribe from $B$ is subtracted because it makes the alternative \textit{less} attractive
						\item Note that we will have to worry about separately identifying the parameters. So for now, will assume $\ve$ does not vary in $z$
					\end{itemize}
			\item Also going to ignore Vote Buyer A's choice for now, so we have
				\[
					v(z) = \alpha -\beta z + \ve - b(z)
				\]
			\item Then the probability that legislator $z$ votes against the new proposal is
				\[
					\Pr\left[v(z)\leq 0 \right] = \Pr\left[\alpha -\beta z + \ve - b(z) \leq 0 \right] 
			                            = \Pr\left[\ve \leq \beta z - \alpha + b(z) \right] 
				\]
				Assuming $\ve \sim \text{Logistic} \ (0,1)$, the probability that legislator $z$ votes ``no'' is $\frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}$.
			\item Take a model with three legislators with ideal points at $z=-\frac{1}{2}$, $z=0$ and $z=\frac{1}{2}$. For ease of notation, let
				\begin{enumerate}
					\item $X = -\alpha + b(0)$ 
					\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
					\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\label{page:sh}$ 
				\end{enumerate}
			\item Then the three probabilities are
				\begin{itemize}
					\item $\frac{1}{1+e^{-\left(- \alpha + b(0) \right)}} = \frac{1}{1+e^{-X}}$, $\frac{1}{1+e^{-\left(\frac{\beta}{2}- \alpha + b(\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Y}}$, $\frac{1}{1+e^{-\left(-\frac{\beta}{2}- \alpha + b(-\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Z}}$
					\item Whether a legislator $z$ votes ``no'' is a random variable, denote it $X(z)$, distributed Bernoulli with this probability:
						\[
							X(z) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}
						\]
				\end{itemize}
		\end{itemize}

\item Vote buyer B
		\begin{itemize}
			\item GS assumption on vote buyers' objective is ``each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP''; this has to be adapted to our situation with uncertainty
			\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
			\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
			\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
			\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
			\item Some legislators who are past FOC point will not be lobbied		
			\item Need to max probability of at least two voting ``no'': $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$
			\item Thus, maximization problem for Vote Buyer B (in absence of Vote Buyer A) is
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(\frac{1}{2}\right)=0\right)  + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
				\end{multline}
			Substituting from the definition of $X$,
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \left(1-\frac{1}{1+e^{-Y}}\right)  + \\
					\frac{1}{1+e^{-Z}} \left(1-\frac{1}{1+e^{-X}}\right) \frac{1}{1+e^{-Y}} + \\
					\left(1-\frac{1}{1+e^{-Z}} \right) \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} + \\
					\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
				\end{multline}
			This can be simplified as 
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} +
					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-Z}} + \\
					\frac{1}{1+e^{-Y}} \frac{1}{1+e^{-Z}} - 2	\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
					\label{eq:obj}
				\end{multline}

			The FOC wrt to $b\left(-\frac{1}{2}\right)$ is 
				\begin{equation}
					W_B \biggl[ \left( \frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2 \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \right) \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
				\end{equation}
			Simplifying:
				\begin{equation}
					W_B \biggl[ \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
					\label{eq:logistic}
				\end{equation}
			Further math related to this equation is on Page~\pageref{eq:logistic2}.
			\item If we divide through by 2, the left side is the average minus the product
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
		\end{itemize}
	\item Vote Buyer A
\end{enumerate}

\section{Adding Non-negativity Constraints for Bribes}
The Lagrangian for the problem is the same as Expression~\ref{eq:obj}, adding on $\lambda_X b\left(0\right) + \lambda_Y b\left(\frac{1}{2}\right) + \lambda_Z b\left(-\frac{1}{2}\right)$

>>>>

\newpage
\section{Solving the Model}
\label{sec:solve}
Backward induction (legislature moves last; B makes last bribe; A makes first bribe)
\begin{enumerate}
	\item Legislature
		\begin{itemize}
			\item Each legislator $z$ will decide whether to vote for $x$ or $s$ given $z$, $a(z)$ and $b(z)$. Votes for $x$ if
			  \[
				  v(z) = \alpha -\beta z + \ve_z + a(z) - b(z)
				\]
				(whether the inequality is weak or strict depends on tie-breaking rules set out in the paper)
					\begin{itemize}
						\item Notice that a bribe from $B$ is subtracted because it makes the alternative \textit{less} attractive
						\item Note that we will have to worry about separately identifying the parameters. So for now, will assume $\ve$ does not vary in $z$
					\end{itemize}
			\item Also going to ignore Vote Buyer A's choice for now, so we have
				\[
					v(z) = \alpha -\beta z + \ve - b(z)
				\]
			\item Then the probability that legislator $z$ votes against the new proposal is
				\[
					\Pr\left[v(z)\leq 0 \right] = \Pr\left[\alpha -\beta z + \ve - b(z) \leq 0 \right] 
			                            = \Pr\left[\ve \leq \beta z - \alpha + b(z) \right] 
				\]
				Assuming $\ve \sim \text{Logistic} \ (0,1)$, the probability that legislator $z$ votes ``no'' is $\frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}$.
			\item Take a model with three legislators with ideal points at $z=-\frac{1}{2}$, $z=0$ and $z=\frac{1}{2}$. For ease of notation, let
				\begin{enumerate}
					\item $X = -\alpha + b(0)$ 
					\item $Y = \frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
					\item $Z = -\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)\label{page:sh}$ 
				\end{enumerate}
			\item Then the three probabilities are
				\begin{itemize}
					\item $\frac{1}{1+e^{-\left(- \alpha + b(0) \right)}} = \frac{1}{1+e^{-X}}$, $\frac{1}{1+e^{-\left(\frac{\beta}{2}- \alpha + b(\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Z}}$, $\frac{1}{1+e^{-\left(-\frac{\beta}{2}- \alpha + b(-\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Y}}$
					\item Whether a legislator $z$ votes ``no'' is a random variable, denote it $X(z)$, distributed Bernoulli with this probability:
						\[
							X(z) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}
						\]
				\end{itemize}
		\end{itemize}

\item Vote buyer B
		\begin{itemize}
			\item GS assumption on vote buyers' objective is ``each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP''; this has to be adapted to our situation with uncertainty
			\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
			\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
			\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
			\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
			\item Some legislators who are past FOC point will not be lobbied		
			\item Need to max probability of at least two voting ``no'': $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$
			\item Thus, maximization problem for Vote Buyer B (in absence of Vote Buyer A) is
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(\frac{1}{2}\right)=0\right)  + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
				\end{multline}
			Substituting from the definition of $X$,
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \left(1-\frac{1}{1+e^{-Y}}\right)  + \\
					\frac{1}{1+e^{-Z}} \left(1-\frac{1}{1+e^{-X}}\right) \frac{1}{1+e^{-Y}} + \\
					\left(1-\frac{1}{1+e^{-Z}} \right) \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} + \\
					\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
				\end{multline}
			This can be simplified as 
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} +
					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-Z}} + \\
					\frac{1}{1+e^{-Y}} \frac{1}{1+e^{-Z}} - 2	\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
					\label{eq:objb}
				\end{multline}

			The FOC wrt to $b\left(\frac{1}{2}\right)$ is 
				\begin{equation}
					W_B \biggl[ \left( \frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2 \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \right) \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
				\end{equation}
			Simplifying:
				\begin{equation}
					W_B \biggl[ \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
					\label{eq:logistic}
				\end{equation}
			Further math related to this equation is on Page~\pageref{eq:logistic2}.
			\item If we divide through by 2, the left side is the average minus the product
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
		\end{itemize}
	\item Vote Buyer A
		\begin{itemize}
			\item Vote buyer A's objective function is identical in form to that of Vote Buyer B (Expression~\ref{eq:objb} 
			  \begin{multline}
			    \max_{a\left(-\frac{1}{2}\right), a\left(0\right), a\left(\frac{1}{2}\right)} 
					W_A \biggl[ \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y}} +
					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-Z}} + \\
					\frac{1}{1+e^{-Y}} \frac{1}{1+e^{-Z}} - 2	\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a(j)
					\label{eq:obja}
				\end{multline}
				where 
				\begin{enumerate}
					\item $X_A = \alpha - b(0,a(0)) + a(0)$ 
					\item $Y_A = -\frac{\beta}{2} + \alpha - b\left(-\frac{1}{2},a\left(-\frac{1}{2}\right)\right)+ a\left(-\frac{1}{2}\right)$
					\item $Z_A = \frac{\beta}{2} + \alpha - b\left(\frac{1}{2},a\left(\frac{1}{2}\right)\right)+ a\left(\frac{1}{2}\right)$
				\end{enumerate}
		\end{itemize}
\end{enumerate}

\newpage
\section{Adding Non-negativity Constraints for Bribes}
\label{sec:nonneg}
The Lagrangian for the problem is the same as Expression~\ref{eq:objb}, adding on $\lambda_X b\left(0\right) + \lambda_Y b\left(\frac{1}{2}\right) + \lambda_Z b\left(-\frac{1}{2}\right)$
